\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer Intern} % Job title
    {Sierra Nevada Corporation} % Organization
    {Sparks, NV} % Location
    {June 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Incoming Software Engineer Intern}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Wahoo Fitness} % Organization
    {Reno, NV} % Location
    {January 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed new functionalities as well as documented and tested new software application.}
        \item {Worked with the software team to coordinate development of new features and resolve issues surrounding ongoing features.}
        \item { Conducted code reviews and submitted feedback and evaluation.}
        \item { Utilized Git, Jira, TestRail, Docker, Selenium, Bitrise, Kobiton, Node.js, JavaScript, TypeScript, AngularJS.}
      \end{cvitems}
    }
 \newcommand{\SubItem}[1]{
        {\setlength\itemindent{15pt} \item[-] #1}
    }
  \cventry
    {Full Stack Developer (Student)} % Job title
    {University of Nevada, Reno} % Organization
    {Reno, NV} % Location
    {August 2018 - January 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on NSF funded projects:}
        \SubItem{RET Site: Cyber Security Initiative for Nevada Teachers (CSINT)}
        \SubItem{CyberCorps(R): "Collaborative Research: Capacity building in Cybersecurity-literacy: An inter-disciplinary approach}
        \item {Worked primarily with developing front end website architecture and designing user interactions on different web pages.}
        \item {Resolved 50+ critical bugs in some of the already completed work when working on the back-end website applications by adopting JavaScript, and Angular.js }
      \end{cvitems}
    }

  \cventry
    {Teaching Assistant (Senior Capstone)} % Job title
    {University of Nevada, Reno} % Organization
    {Reno, NV} % Location
    {November 2016 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Assisted professors and primarily lecturers in lecturing, grading, advising and course maintenance.}
		\item {  Tasked with automating student purchasing system by adopting SQL (MySQL), JavaScript and Python programming language to design a new tracking system.}
		\item {  Managed purchase orders of over 150 students (per year), and worked with retail analytics and projects teams to ensure all project works were handled as per best practices.}
		\item {  Analyzed all courses' documents for accuracy and updated the courses' management system to reflect any changes made.}
      \end{cvitems}
    }

\end{cventries}
